Discrete Time Markov Model

### 2025-04-03 analysis/discrete-markov.qmd
Updating DT model

---
title: "Discrete Time Markov Model"
subtitle: "Examining the Association Between Procrastination and Cognitive Transitions"
---

# Setting up {.unnumbered}

## Loading packages {.unnumbered}

@@

## Loading functions {.unnumbered}

@@

@@

@@

plot_predictions_stationary <- function(predictions) {
  # Visualizes predicted transition probabilities from stationary multi-state models.
  # Shows probability curves by procrastination level, stratified by baseline state.
  # Arguments:
  #   - predictions: Tidy predictions from tidy_predictions()
  # Returns:
  #   - Faceted ggplot showing predicted probability curves
  # 
  predictions |>
    ggplot(aes(x = Total_p, y = prob, colour = status_prev)) +
    geom_line(linewidth = 1) +
    ggokabeito::scale_colour_okabe_ito() +
    labs(
      title = "Predicted transition probabilities (stationary model)",
      # subtitle = "According to previous cognitive state",
      x = "Total Procrastination", y = "Probability", colour = "Previous State") +
    facet_wrap(~ status, labeller = labeller(
      status = function(x){paste0("Transition to: ", x)}
    ))
}

get_time_varying_matrix <- function(model, time_point) {
  expand.grid(
    Gender = factor(0),
    Total_p = mean(data_stack$Total_p),
    status_prev = factor(1:3),
    wave = time_point) |> 
    modelr::add_predictions(model, var = "prob", type = "probs") |> 
    select(status_prev, starts_with("prob")) |> 
    mutate(
      status_prev = factor(status_prev, labels = state_names),
      across(starts_with("prob"), ~round(., 3))) |>
    tibble::column_to_rownames("status_prev") |>
    as.matrix() |> `colnames<-`(state_names)
}
```

## Setting theme {.unnumbered}

@@

```{r stack-data}
data_stack <- data_stack |>
  mutate(status_prev = lag(status), .after = status) |>
  ungroup() |> 
  filter(wave != 2016, !is.na(Total_p))

@@

tran_df <- transition_matrix_observed |>
  as.data.frame() |>
  mutate(
    from_state = factor(c("Normal cognition", "MCI", "Dementia"),
                        levels = c("Normal cognition", "MCI", "Dementia"))
    ) |>
  reshape2::melt(
    id.vars = "from_state", variable.name = "to_state", value.name = "probability") |>
  mutate(
    to_state = factor(to_state, levels = rev(levels(to_state)))
    )

fig_2 <- tran_df |>
  ggplot(aes(x = from_state, y = to_state, fill = probability)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(
    aes(label = format(round(probability, 3), nsmall = 3)),
    size = 4.5, 
    color = "#212427",
    fontface = "bold") +
  colorspace::scale_fill_continuous_diverging(
    palette = "Blue-Red 3", mid = 0.50, alpha = 0.5, 
    limits = c(0, 1), name = "Transition \nProbability") +
  labs(title = "Transition Probabilities Across Cognitive States",
       subtitle = "Observed state transitions between assessment waves",
       x = "Previous State (t - 1)", 
       y = "Current State (t)") +
  theme(
    axis.text = element_text(size = 10),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
    legend.position = "right",
    legend.text = element_text(size = 9),
    panel.grid = element_blank()
  )

fig_2
```

@@

```{r model-fitting}
#| code-fold: true
#| code-summary: "Check out my models"
#| 
# Baseline model (only gender)
fit_1 <- nnet::multinom(
  status ~ Gender, family = multinomial, 
  data = data_stack, trace = FALSE)

# With procrastination
fit_2 <- nnet::multinom(
  status ~ Gender + Total_p, family = multinomial, 
  data = data_stack, trace = FALSE)

# Full model with previous state
fit_3 <- nnet::multinom(
  status ~ Gender + Total_p + status_prev, family = multinomial, 
  data = data_stack, trace = FALSE)
```

@@

```{r model-comparison}
anova(fit_1, fit_2, fit_3) |>
  knitr::kable(caption = "Nested Model Comparison") |>
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE)
```

@@

```{r model-output}
#| code-fold: true
#| code-summary: "Check out my code"
#| 
broom::tidy(fit_3) |>
  filter(term != "(Intercept)") |>
  mutate(
    y.level = case_when(
      y.level == "2" ~ "NC - MCI",
      y.level == "3" ~ "NC - Dementia"),
    term = case_when(
      term == "Gender1" ~ "Being female",
      term == "Total_p" ~ "Procrastination",
      term == "status_prev2" ~ "Previous state: MCI",
      term == "status_prev3" ~ "Previous state: Dementia",
      TRUE ~ term)
    ) |>
  mutate(across(c(estimate:p.value), ~ round(x = ., digits = 3)))
```

@@

Let's visualize the predicted transition probabilities from the stationary models. We will show probability curves by procrastination level

```{r}
#| code-fold: true
#| code-summary: "Check out my code"
#| fig-width: 12
#| label: fig-model-predictions
#| fig-cap: "Predicted transition probabilities from the stationary model."
#| 
## Making a prediction dataset -------------------------------------------------
pred_data <- expand.grid(
  Gender = factor(0),
  status_prev = levels(data_stack$status_prev),
  Total_p = seq(0, 60, length = 200))

## Plotting predictions
fig_3 <- pred_data |>
  modelr::add_predictions(model = fit_3, var = "pred", type = "probs") |>
  tidy_predictions() |>
  plot_predictions_stationary()

@@

# Getting estimated probabilities
estimated_probs <- expand.grid(
  Gender = factor(0),
  Total_p = mean(data_stack$Total_p),
  status_prev = states) |>
  modelr::add_predictions(model = fit_3, var = "pred", type = "probs")

@@

tran_df_estimate <- transition_matrix_estimated |>
  as.data.frame() |>
  mutate(from_state = factor(
    c("Normal cognition", "MCI", "Dementia"),
    levels = c("Normal cognition", "MCI", "Dementia")
  )) |>
  reshape2::melt(id.vars = "from_state",
                 variable.name = "to_state",
                 value.name = "probability") |>
  mutate(to_state = factor(to_state, levels = rev(levels(to_state))))

fig_4 <- tran_df_estimate |>
  ggplot(aes(x = from_state, y = to_state, fill = probability)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(
    aes(label = format(round(probability, 3), nsmall = 3)),
    size = 4.5, 
    color = "#212427",
    fontface = "bold") +
  colorspace::scale_fill_continuous_diverging(
    palette = "Blue-Red 3", mid = 0.50, alpha = 0.5, 
    limits = c(0, 1), name = "Transition \nProbability") +
  labs(title = "Transition Probabilities Across Cognitive States",
       subtitle = "Estimated state transitions between assessment waves",
       x = "Previous State (t - 1)", 
       y = "Current State (t)") +
  theme(
    axis.text = element_text(size = 10),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
    legend.position = "right",
    legend.text = element_text(size = 9),
    panel.grid = element_blank()
  )

fig_2 + fig_4 + plot_layout(axis_titles = "collect", guides = "collect")
```

@@

# Model 4: Additive time effects
fit_4 <- nnet::multinom(
  status ~ Gender + Total_p + status_prev + wave, family = multinomial, 
  data = data_stack, trace = FALSE)

# Model 5: State-specific time effects
fit_5 <- nnet::multinom(
  status ~ Gender + Total_p + (status_prev * wave), family = multinomial, 
  data = data_stack, trace = FALSE)

# Model 6: Full time interactions
fit_6 <- nnet::multinom(
  status ~ (Gender + Total_p + status_prev) * wave, family = multinomial, 
  data = data_stack, trace = FALSE)
```

@@

```{r}
#| code-fold: true
#| code-summary: "Check out my code"
#| layout-nrow: 2

# Fit statistics
models <- list(
  "Stationary" = fit_3,
  "Additive Time" = fit_4,
  "State-Time Interaction" = fit_5,
  "Full Interactions" = fit_6
)

# Create comparison table
comparison_table <- purrr::map_dfr(models, broom::glance, .id = "Model") |>
  select(Model:AIC) |>
  mutate(across(where(is.numeric), \(x) round(x, digits = 1)))

# Likelihood ratio tests
lr_tests <- anova(fit_3, fit_4, fit_5, fit_6)

# Outputting tables
knitr::kable(lr_tests, caption = "Likelihood Ratio Tests") |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))

knitr::kable(comparison_table, caption = "Model Fit Statistics") |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
```

@@

```{r non-stationary-output}
#| code-fold: true
#| code-summary: "Check out my code"

broom::tidy(fit_4) |>
  filter(term != "(Intercept)") |>
  mutate(
    y.level = case_when(
      y.level == "2" ~ "NC - MCI",
      y.level == "3" ~ "NC - Dementia"),
    term = case_when(
      term == "Gender1" ~ "Being female",
      term == "Total_p" ~ "Procrastination",
      term == "status_prev2" ~ "Previous state: MCI",
      term == "status_prev3" ~ "Previous state: Dementia",
      term == "wave" ~ "Time",
      TRUE ~ term)
    ) |>
  mutate(across(c(estimate:p.value), ~ round(x = ., digits = 3)))
```

@@

```{r non-stationary-visualise}
#| code-fold: true
#| code-summary: "Check our my code"
#| fig-width: 12
#| fig-height: 10
#| label: fig-non-stationary
#| fig-cap: "Predicted transition probabilities from the non-stationary model."
#| 
expand.grid(
  Gender = factor(0),
  status_prev = levels(data_stack$status_prev),
  Total_p = seq(0, 60, length = 200),
  wave = unique(data_stack$wave)) |>
  modelr::add_predictions(model = fit_4, var = "pred", type = "probs") |>
  tidy_predictions() |>
  mutate(wave = factor(wave)) |>
  ggplot(aes(x = Total_p, y = prob, color = status_prev)) +
  geom_line(linewidth = 1) +
  ggokabeito::scale_color_okabe_ito() +
  labs(
    title = "Time-Varying Transition Probabilities",
    x = "Total Procrastination", 
    y = "Predicted Probability", color = "Previous State") +
  facet_grid(wave ~ status, labeller = labeller(
    wave = function(x) paste("Years since baseline:", x),
    status = function(x) paste("Transition to:", x)
  )) +
  theme(panel.spacing = unit(1, "lines"))

@@

# Get matrices for all time points
time_varying_matrices <- purrr::map(
  setNames(time_points, paste(time_points, "Years")),
  ~ get_time_varying_matrix(fit_4, .x)
)

>>>>

---
title: "Discrete Time Markov Model"
---

# Setting up

## Loading packages

@@

## Loading functions

@@

reshape_matrix <- function(matrix) {
  # Converts a transition probability matrix into a tidy format suitable for visualization.
  # Transforms the matrix into long format with explicit factor levels for cognitive states,
  # preserving the original ordering while preparing for ggplot compatibility.
  # Arguments:
  #   - matrix: A square transition probability matrix with states as row/column names
  # Returns:
  #   - Tidy data frame with columns:
  #     * from_state: Factor indicating origin cognitive state
  #     * to_state: Factor indicating destination cognitive state (reversed for plotting)
  #     * probability: Numeric transition probability values

  matrix |>
    as.data.frame() |>
    mutate(
      from_state = factor(c(
        "Normal cognition", "MCI", "Dementia"),
        levels = c("Normal cognition", "MCI", "Dementia"))
    ) |>
    reshape2::melt(
      id.vars = "from_state", 
      variable.name = "to_state", 
      value.name = "probability") |>
    mutate(to_state = factor(to_state, levels = rev(levels(to_state))))
}

plot_transition_matrix <- function(matrix, observed = TRUE) {
  # Creates a heatmap visualization of cognitive state transition probabilities.
  # Generates either observed or estimated transition plots with consistent formatting,
  # including labeled probability values and a diverging color scale for emphasis.
  # Arguments:
  #   - matrix: Tidy transition matrix from reshape_matrix()
  #   - observed: Logical flag indicating whether data represents observed (TRUE) 
  #               or estimated (FALSE) transitions
  # Returns:
  #   - ggplot heatmap object with:
  #     * State transitions as cells
  #     * Probability values displayed numerically
  #     * Custom color scale and axis formatting

  if(observed == TRUE) {
    subtitle <- "Observed state transitions between assessment waves"
  } else {
    subtitle <- "Estimated state transitions between assessment waves"
  }

  matrix |>
    ggplot(aes(x = from_state, y = to_state, fill = probability)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(
      aes(label = format(round(probability, 3), nsmall = 3)),
      size = 4.5, 
      color = "#212427",
      fontface = "bold") +
    colorspace::scale_fill_continuous_diverging(
      palette = "Blue-Red 3", mid = 0.50, alpha = 0.5, 
      limits = c(0, 1), name = "Transition \nProbability") +
    labs(title = "Transition Probabilities Across Cognitive States",
         subtitle = subtitle,
         x = "Previous State (t - 1)", 
         y = "Current State (t)") +
    theme(
      axis.text = element_text(size = 10),
      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
      legend.position = "right",
      legend.text = element_text(size = 9),
      panel.grid = element_blank()
    )
}

@@

tidy_output <- function(fit) {
  output <- broom::tidy(fit, conf.int = TRUE) |>
    filter(term != "(Intercept)") |>
    mutate(
      term = case_when(
      term == "Gender1" ~ "Being female",
      term == "Education_tri1" ~ "High school degree vs. No education",
      term == "Education_tri2" ~ "Further education vs. No education",
      term == "Total_dep_2016" ~ "Depression Scores (2016)",
      term == "Total_p" ~ "Procrastination",
      term == "status_prev2" ~ "Previous state: MCI",
      term == "status_prev3" ~ "Previous state: Dementia",
      term == "wave" ~ "Time",
      TRUE ~ term)) |>
  mutate(across(c(estimate:p.value), ~ round(x = ., digits = 3)))

  if(any(output$y.level == "1")) {
    output |>
      mutate(y.level = case_when(
      y.level == "1" ~ "MCI - NC",
      y.level == "3" ~ "MCI - Dementia"))
  } else {
    output |>
      mutate(y.level = case_when(
      y.level == "2" ~ "NC - MCI",
      y.level == "3" ~ "NC - Dementia"))
  }
}

@@

plot_predictions_stationary <- function(predictions, variable, x_axis) {
  # Visualizes predicted transition probabilities from stationary multi-state models.
  # Shows probability curves by procrastination level, stratified by baseline state.
  # Arguments:
  #   - predictions: Tidy predictions from tidy_predictions()
  # Returns:
  #   - Faceted ggplot showing predicted probability curves
  # 
  predictions |>
    ggplot(aes(x = {{variable}}, y = prob, colour = status_prev)) +
    geom_line(linewidth = 1) +
    ggokabeito::scale_colour_okabe_ito() +
    labs(
      title = "Predicted transition probabilities (stationary model)",
      x = x_axis, y = "Probability", colour = "Previous State") +
    facet_wrap(~ status, labeller = labeller(
      status = function(x){paste0("Transition to: ", x)}
    ))
}

get_time_varying_matrix <- function(model, time_point) {
  expand.grid(
    Gender = factor(0),
    Age = mean(data_stack$Age),
    Education_tri = factor(0),
    Total_dep_2016 = mean(data_stack$Total_dep_2016),
    Total_p = mean(data_stack$Total_p),
    status_prev = factor(1:3),
    wave = time_point) |> 
    modelr::add_predictions(model, var = "prob", type = "probs") |> 
    select(status_prev, starts_with("prob")) |> 
    mutate(
      status_prev = factor(status_prev, labels = state_names),
      across(starts_with("prob"), ~round(., 3))) |>
    tibble::column_to_rownames("status_prev") |>
    as.matrix() |> `colnames<-`(state_names)
}
```

## Setting theme

@@

```{r stack-data}
data_stack <- data_stack |>
  mutate(status_prev = lag(status), .after = status) |>
  ungroup() |> 
  filter(wave != 2016, !is.na(Total_p), Age >= 50)

@@

fig_3 <- transition_matrix_observed |>
  reshape_matrix() |>
  plot_transition_matrix()

@@

```{r model-fitting}
#| code-fold: true
#| code-summary: "Check out my models"
#| 
# Baseline model (only gender; reference: NC)
fit_1a <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Total_dep_2016, family = multinomial, 
  data = data_stack, trace = FALSE)

# Baseline model (only gender; reference: MCI)
fit_1b <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Total_dep_2016, family = multinomial, 
  data = data_stack |> mutate(status = relevel(status, ref = 2)), 
  trace = FALSE)

# With procrastination (reference: NC)
fit_2a <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Total_dep_2016 + Total_p, family = multinomial, 
  data = data_stack, trace = FALSE)

# With procrastination (reference: MCI)
fit_2b <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Total_dep_2016 + Total_p, family = multinomial, 
  data = data_stack |> mutate(status = relevel(status, ref = 2)), 
  trace = FALSE)

# Full model with previous state (reference NC)
fit_3a <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Total_dep_2016 + Total_p + status_prev, family = multinomial, 
  data = data_stack, trace = FALSE)

# Full model with previous state (reference MCI)
fit_3b <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Total_dep_2016 + Total_p + status_prev, family = multinomial, 
  data = data_stack |> mutate(status = relevel(status, ref = 2)), 
  trace = FALSE)
```

@@

```{r model-comparison}
anova(fit_1a, fit_2a, fit_3a) |>
  knitr::kable(caption = "Nested Model Comparison") |>
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE)
```

@@

Below we present the estimated parameters for the stationary models. We will transform the estimates to odds ratios and code them based on significance.

```{r model-output}
#| code-fold: true
#| code-summary: "Check out my code"
#| 
stationary_results <- rbind(tidy_output(fit_3a), tidy_output(fit_3b)) |>
  mutate(
    # Transforming to odds ratios
    estimate = exp(estimate),
    conf.low = exp(conf.low),
    conf.high = exp(conf.high),

    # Mutating to factors
    y.level = factor(
      y.level, 
      levels = c("NC - MCI", "MCI - NC", 
                 "NC - Dementia", "MCI - Dementia")),
    term = factor(
      term, 
      levels = c("Being female", "Age", "High school degree vs. No education",
                 "Further education vs. No education", "Depression Scores (2016)",
                 "Procrastination", "Previous state: MCI", "Previous state: Dementia")),

    # Creating a colour code
    positive = case_when(
      estimate > 1 & p.value < 0.05 ~ "Positive",
      estimate < 1 & p.value < 0.05 ~ "Negative",
      TRUE ~ "NS"),

    positive = factor(positive, levels = c("Positive", "Negative", "NS"))
    )

head(stationary_results)
```

@@

Let's visualise the estimated odds ratios (@fig-odds-ratio) and the predicted transition probabilities (@fig-model-predictions) for the stationary model .

```{r}
#| message: false
#| warning: false
#| code-fold: true
#| code-summary: "Check out my code"
#| fig-width: 12
#| label: fig-odds-ratio
#| fig-cap: "Estimated odds ratios for the stationary model."

fig_4a <- stationary_results |>
  filter(!term %in% c("Previous state: MCI", "Previous state: Dementia")) |>
  ggplot(aes(x = estimate, y = y.level, colour = positive)) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "gray50") +
  ggstance::geom_pointrangeh(
    aes(xmin = conf.low, xmax = conf.high),
    position = ggstance::position_dodgev(height = 0.5),
    size = 1.25,
    fatten = 3) +
  scale_colour_manual(values = c(
    "Positive" = "#0072B2", 
    "Negative" = "#E69F00", 
    "NS"       = "#B2BEB5")) +
  labs(title = "Odds Ratios from Multinomial Model",
       x = "Odds Ratio", y = "Predictor") +
  guides(colour = "none") +
  facet_wrap(~ term, scales = "free_x") +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12, face = "bold"),
    strip.text = element_text(size = 10, face = "bold"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank())

fig_4a
```

```{r}
#| code-fold: true
#| code-summary: "Check out my code"
#| fig-width: 12
#| label: fig-model-predictions
#| fig-cap: "Predicted transition probabilities from the stationary model."
#| 
## Making a prediction dataset -------------------------------------------------
pred_data <- expand.grid(
  Gender = factor(0),
  Age = mean(data_stack$Age),
  Education_tri = factor(0),
  Total_dep_2016 = mean(data_stack$Total_dep_2016),
  status_prev = levels(data_stack$status_prev),
  Total_p = seq(0, 60, length = 200))

## Plotting predictions
fig_4b <- pred_data |>
  modelr::add_predictions(model = fit_3a, var = "pred", type = "probs") |>
  tidy_predictions() |>
  plot_predictions_stationary(variable = Total_p, x_axis = "Total Procrastination")

fig_4b
```

@@

# Getting estimated probabilities
estimated_probs <- expand.grid(
  Gender = factor(0),
  Age = mean(data_stack$Age),
  Education_tri = factor(0),
  Total_dep_2016 = mean(data_stack$Total_dep_2016),
  Total_p = mean(data_stack$Total_p),
  status_prev = states) |>
  modelr::add_predictions(model = fit_3a, var = "pred", type = "probs")

@@

fig_5 <- transition_matrix_estimated |>
  reshape_matrix() |>
  plot_transition_matrix(observed = FALSE)

fig_3 + fig_5 + plot_layout(axis_titles = "collect", guides = "collect")
```

@@

# Model 4: Additive time effects
fit_4a <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Total_dep_2016 + Total_p + status_prev + wave, family = multinomial, 
  data = data_stack, trace = FALSE)

fit_4b <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Total_dep_2016 + Total_p + status_prev + wave, family = multinomial, 
  data = data_stack |> mutate(status = relevel(status, ref = 2)), 
  trace = FALSE)

# Model 5: State-specific time effects
fit_5a <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Total_dep_2016 + Total_p + (status_prev * wave), family = multinomial, 
  data = data_stack, trace = FALSE)

fit_5b <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Total_dep_2016 + Total_p + (status_prev * wave), family = multinomial, 
  data = data_stack |> mutate(status = relevel(status, ref = 2)), 
  trace = FALSE)

# Model 6: Full time interactions
fit_6a <- nnet::multinom(
  status ~ (Gender + Age + Education_tri + Total_dep_2016 + Total_p + status_prev) * wave, family = multinomial, 
  data = data_stack, trace = FALSE)

fit_6b <- nnet::multinom(
  status ~ (Gender + Age + Education_tri + Total_dep_2016 + Total_p + status_prev) * wave, family = multinomial, 
  data = data_stack |> mutate(status = relevel(status, ref = 2)), 
  trace = FALSE)
```

@@

```{r non-stationary-goodness}
#| code-fold: true
#| code-summary: "Check out my code"
#| layout-nrow: 2

# Fit statistics
models <- list(
  "Stationary" = fit_3a,
  "Additive Time" = fit_4a,
  "State-Time Interaction" = fit_5a,
  "Full Interactions" = fit_6a
)

# Create comparison table
comparison_table <- purrr::map_dfr(models, broom::glance, .id = "Model") |>
  select(edf:AIC) |>
  mutate(across(where(is.numeric), \(x) round(x, digits = 1)))

# Outputting as table
anova(fit_3a, fit_4a, fit_5a, fit_6a) |>
  mutate(
    Model = c("Stationary", "Additive", "State-Time Interactions", "Full Interactions"),
    `Resid. Dev` = round(`Resid. Dev`, digits = 3),
    `LR stat.` = round(`LR stat.`, digits = 3),
    `Pr(Chi)` = round(`Pr(Chi)`, digits = 3)
    ) |>
  cbind(comparison_table) |>
  DT::datatable(
    options = list(
      columnDefs = list(list(className = 'dt-center', targets = "_all"))
    ),
    rownames = FALSE,
    caption = "Likelihood Ratio Tests"
  )
```

@@

```{r non-stationary-output}
non_stationary_results <- rbind(tidy_output(fit_4a), tidy_output(fit_4b))

head(non_stationary_results)
```

@@

```{r non-stationary-visualise}
#| code-fold: true
#| code-summary: "Check our my code"
#| fig-width: 12
#| fig-height: 10
#| label: fig-non-stationary
#| fig-cap: "Predicted transition probabilities from the non-stationary model."
#| 
expand.grid(
  Gender = factor(0),
  Age = mean(data_stack$Age),
  Education_tri = factor(0),
  Total_dep_2016 = mean(data_stack$Total_dep_2016),
  status_prev = levels(data_stack$status_prev),
  Total_p = seq(0, 60, length = 200),
  wave = unique(data_stack$wave)) |>
  modelr::add_predictions(model = fit_4a, var = "pred", type = "probs") |>
  tidy_predictions() |>
  mutate(wave = factor(wave)) |>
  ggplot(aes(x = Total_p, y = prob, color = status_prev)) +
  geom_line(linewidth = 1) +
  ggokabeito::scale_color_okabe_ito() +
  labs(
    title = "Time-Varying Transition Probabilities",
    x = "Total Procrastination", 
    y = "Predicted Probability", color = "Previous State") +
  facet_grid(wave ~ status, labeller = labeller(
    wave = function(x) paste("Years since baseline:", x),
    status = function(x) paste("Transition to:", x)
  )) +
  theme(panel.spacing = unit(1, "lines"))

@@

# Get matrices for all time points
time_varying_matrices <- purrr::map(
  setNames(time_points, paste(time_points, "Years")),
  ~ get_time_varying_matrix(fit_4a, .x)
)
